Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-11 report/report.tex
Update results sections

For the primary collision study.
Table \ref{table:road-collision} shows the statistics of the collision study, and the number of roads, number of edges and total edge length that showed intersections with other features before road extrusion, by road category.
For footpaths in particular, it was shown that 12.05\% of all roads collide with some other feature after extrusion to the minimum width.
The same was shown to be true for 0.11\% of the road polyline edges and 0.09\% of the total road length.
Table \ref{table:road-collision-corrected} shows the remaining roads, edges and total edges length whose intersections with other features could not be resolved by geometrical translation of a distance smaller than the positional accuracy.
For footpaths this was shown to hold of 0.51\% of all roads, 
The number of road edges and percentage of the total road length that could not be corrected by geometric translation was significantly small.

>>>>

For the primary collision study.
Table \ref{table:road-collision} shows the statistics of the collision study, and the number of roads, number of edges and total edge length that showed intersections with other features, by road category.
For footpaths in particular, it was shown that 12.05\% of all roads collide with some other feature after extrusion to the minimum width.
The same was shown to be true for 0.11\% of the road polyline edges and 0.09\% of the total road length.
Table \ref{table:road-collision-corrected} shows the remaining roads, edges and total edges length whose intersections with other features could not be resolved by geometrical translation of a distance smaller than the positional accuracy.
For footpaths this was shown to hold for 0.51\% of all roads, 
The number of road edges and percentage of the total road length that could not be corrected by geometric translation was significantly small.
